\documentclass{article}
\title{Proposal 0: Side-channel Attack on Cache and MMU}
\author{Li Dinghong \\SIST, Shanghaitech University \\27663262}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{tikz}
\usepackage[]{forest}
\usepackage[colorlinks,linkcolor=red]{hyperref}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{subfloat}
\usepackage{pdfpages}
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{xcolor}
\usepackage{colortbl,booktabs}
\usepackage{pict2e}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=20mm,
	top=10mm,
}

\begin{document}
\maketitle
\large

\section{Introduction and Background}{
	Side-channel attacks are widely studied in recent years. Unlike conventional attack models, side-channel attacks rely on gained from the implementation of a computer system, like time, energy and power consumption and electromagnetic leaks, rather than weaknesses in the implemented algorithm itself. 

	Side-channel attacks on address space layout randomization (ASLR), which is usually thought as an important first line of defense against memory corruption attacks have been proposed in \textbf{Gras, et al. 2017}. 
}

% \section{Related Works}{}

\section{Methodology: How is it related to Operating Systems? }{
	There are several different ways to study this topic. For instance, we can propose a novel CPU architecture to raise cache security, or analyze side-channel attacks using information theory. If we want to study it from perspective of operating systems, however, it is better to narrow it to some specific contexts. 

	A good option is to run our models on browsers, as is used in previous works. Most likely, we will test both attack and defense models on three major browsers: Firefox, Safari and Chrome. 

	This attack is highly related to MMU, which is an important part in modern operating systems. 
}

\section{Better Attack Models}{
	Attack models mainly exploit vulnerability of ASLR. 

	Can we have a better attack models? 

	That means, can we get privacy information with higher efficieny or/ and higher accuracy? 
}

\section{Defense Models}{
	Existing defense models include naively disabling cache, or reducing accuracy of timers. However, these methods are very costly. 

	Are there any better defense models? 
}

\section{Tradeoffs between Performance and Security on Cache}{
	We can compare the effectiveness of side-channel attacks on cache with different replacement policies or different cache design. 
}

\end{document}